Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-17 manuscript.Rmd
fixed references and software citations

bibliography      : ["equivalence.bib"]

@@

```{r include = FALSE}
library("papaja")
```

@@

@@

In the remainder of this article we will provide five detailed examples of equivalence tests performed on published studies. These concrete and easy to follow examples will illustrate all approaches to setting equivalence bounds discussed above, and demonstrate how to perform and report equivalence tests. The code to reproduce these analyses is available at <https://osf.io/qamc6/>^[The OSF project contains all necessary files to reproduce examples 1--5 in R, jamovi [@jamovi2017], and in a spreadsheet; as well as a preprint of this manuscript. The manuscript, including the figures and statistical analyses, was created using R version 3.4.2 [@RCoreTeam2017] and RStudio version 1.1.383 [@RStudioTeam2016], with the packages `TOSTER` version 0.3 [@Lakens2017c], `pwr` version 1.2--1 [@Champely2017], `rmarkdown` version 1.7[@Allaire2017], `knitr` version 1.17 [@Xie2017], `papaja` version 0.1.0.9492 [@Aust2017], `ggplot2` version 2.2.1 [@Wickham2009], `gridExtra` version 2.3 [@Auguie2017], `lattice` version 0.20--35 [@Sarkar2008], and `purrr` version 0.2.4 [@Henry2017].].

>>>>

bibliography      : ["equivalence.bib","r-references.bib"]

@@

```{r include = FALSE}
library("papaja")
library("bookdown")
library("rmarkdown")
library("knitr")
library("TOSTER")
library("purrr")
```

@@

```{r include=FALSE}
r_refs(file = "r-references.bib")
my_citation <- cite_r(file = "r-references.bib")
```

@@

In the remainder of this article we will provide five detailed examples of equivalence tests performed on published studies. These concrete and easy to follow examples will illustrate all approaches to setting equivalence bounds discussed above, and demonstrate how to perform and report equivalence tests. The code to reproduce these analyses is available at <https://osf.io/qamc6/>^[The OSF project contains all necessary files to reproduce examples 1--5 in R, jamovi [@jamovi2017], and in a spreadsheet; as well as a preprint of this manuscript. The manuscript, including the figures and statistical analyses, was created using RStudio [1.1.383, @RStudioTeam2016] and `r my_citation`].
